Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-03-27 doc/JFM2022/Final/main_jfm.tex
updates

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}

%
\usepackage[justification=justified]{caption}

@@

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}
\newcommand{\ReviewerOne}[1]{\textcolor{red}{#1}}
\newcommand{\ReviewerTwo}[1]{\textcolor{green}{#1}}
\newcommand{\ReviewerThree}[1]{\textcolor{magenta}{#1}}

@@

Our future goals include extending the current framework to a
three-dimensional JP vesicle system. This will require additional
algorithmic implementation including a fast summation method such as the
fast multipole method. Other research directions include
fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
%introduce thermal fluctuations into the model. 
%This will result in Janus particles that include Brownian motion, 
critical to understanding membrane diffusion,
and an analysis of the relationship between particle shape on effective
properties.
Finally, more
physical boundary conditions for the HAP model will allow us to draw
comparisons between computational and laboratory experiments.

\begin{acknowledgments}
  {\bf Acknowledgments:} B.Q.~acknowledges support from NSF (Grant
  No.~DMS 2012560) and from the Simons Foundation, Mathematics and
  Physical Sciences-Collaboration Grants for Mathematicians (Award
  No.~527139). Y.-N. Y.~acknowledges support from NSF (Grant No.~DMS 1614863 and 1951600) and
  Flatiron Institute, part of Simons Foundation.
%We would like to acknowledge 
\end{acknowledgments}

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}
\usepackage{orcidlink}
%
\usepackage[justification=justified]{caption}

@@

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}
\newcommand{\ReviewerOne}[1]{\textcolor{red}{#1}}
\newcommand{\ReviewerTwo}[1]{\textcolor{green}{#1}}
\newcommand{\ReviewerThree}[1]{\textcolor{magenta}{#1}}
\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}

@@

Our future goals include extending the current framework to a
three-dimensional JP vesicle system. This will require additional
algorithmic implementation including a fast summation method such as the
fast multipole method. Other research directions include
fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
%introduce thermal fluctuations into the model. 
%This will result in Janus particles that include Brownian motion, 
critical to understanding membrane diffusion,
and an analysis of the relationship between particle shape on effective
properties.
Finally, more
physical boundary conditions for the HAP model will allow us to draw
comparisons between computational and laboratory experiments.\\

%\begin{acknowledgments}
\noindent
  {\bf Funding.} B.Q.~acknowledges support from NSF (Grant
  No.~DMS 2012560) and from the Simons Foundation, Mathematics and
  Physical Sciences-Collaboration Grants for Mathematicians (Award
  No.~527139). Y.-N. Y.~acknowledges support from NSF (Grant No.~DMS 1614863 and 1951600) and Flatiron Institute, part of Simons Foundation.\\

  \noindent
  {\bf Declaration of interests.} The authors report no conflict of interest.\\

  \urlstyle{rm}

\noindent
{\bf Author ORCIDs.}\\
\orcidlink{0000-0003-0140-1909} Szu-Pei Fu  {\url{https://orcid.org/0000-0003-0140-1909}}\\
\orcidlink{0000-0002-9186-8926} Bryan Quaife {\url{https://orcid.org/0000-0002-9186-8926}}\\  
\orcidlink{0000-0003-1626-7052} Rolf Ryham {\url{https://orcid.org/0000-0003-1626-7052}}\\  
\orcidlink{0000-0001-9771-5480} Yuan-Nan Young  {\url{https://orcid.org/0000-0001-9771-5480 }}

%We would like to acknowledge 
%\end{acknowledgments}
